Using a Rover's Active Suspension System as a 2-Axis Solar Tracker Mechanism

### 2020-06-12 article.tex
replaced 'thesis' to 'paper'.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The findings of this thesis support using the SherpaTT rover active suspension system as a mechanism for solar panel inclination and orientation under certain \ac{SA} sizing conditions. Combining a maximum attainable \ac{SA} surface inclination angle of \SI{10}{\degree} with optimal daily orientation angles results in appreciable traverse gains when compared to what is obtained from a horizontal surface. However, this is not true for large \ac{SA} areas. Furthermore, the smaller the required solar cell coverage area the greater the gains. In light of this, \ac{SA} sizing for the the worst case daily insolations introduce a hibernation mode solar power draw constraint of \SI{17}{\watt} near the equator at \SI{2}{\degree}S and \SI{15}{\watt} in the northern hemisphere at \SI{34}{\degree}N. With these power budgets, an average traverse gain of \SI{34}{\percent} is achieved at \SI{2}{\degree}S for a clear day with a $\tau$ factor of 0.4. At \SI{34}{\degree}N, the average gain is \SI{25}{\percent} under the same atmospheric opacity. These gains remain significant on dusty days at \SI{23}{\percent} and \SI{10}{\percent} at respective latitudes with a $\tau$ factor of 1.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The findings of this paper support using the SherpaTT rover active suspension system as a mechanism for solar panel inclination and orientation under certain \ac{SA} sizing conditions. Combining a maximum attainable \ac{SA} surface inclination angle of \SI{10}{\degree} with optimal daily orientation angles results in appreciable traverse gains when compared to what is obtained from a horizontal surface. However, this is not true for large \ac{SA} areas. Furthermore, the smaller the required solar cell coverage area the greater the gains. In light of this, \ac{SA} sizing for the the worst case daily insolations introduce a hibernation mode solar power draw constraint of \SI{17}{\watt} near the equator at \SI{2}{\degree}S and \SI{15}{\watt} in the northern hemisphere at \SI{34}{\degree}N. With these power budgets, an average traverse gain of \SI{34}{\percent} is achieved at \SI{2}{\degree}S for a clear day with a $\tau$ factor of 0.4. At \SI{34}{\degree}N, the average gain is \SI{25}{\percent} under the same atmospheric opacity. These gains remain significant on dusty days at \SI{23}{\percent} and \SI{10}{\percent} at respective latitudes with a $\tau$ factor of 1.
